### 2018-09-18 README.Rmd
update the readme

From start to finish, the repository is divided into several experiments, each with their own scripts and results. These are accompanied by documentation using github READMEs and can be easily explored by going to the appropriate folders:

@@

* manuscript: source files for producing the manuscript
* package: an R package with several helper functions
* data: raw data files required by the scripts
* derived: intermediate data files produced by the scripts

@@

* **The performance of methods** used in [dynguidelines](https://www.github.com/dynverse/dynguidelines). _Not yet available_

>>>>

From start to finish, the repository is divided into several experiments, each with their own scripts and results. These are accompanied by documentation using github readmes and can thus be easily explored by going to the appropriate folders:

@@

* [Manuscript](manuscript): Source files for producing the manuscript.
* [Package](package): An R package with several helper functions.
* [Data](data): Raw data files required by the scripts.
* [Derived](derived): Intermediate data files produced by the scripts. These files or not git committed.

@@

* **The performance of methods** used for the [results overview figure](`r dynbenchmark::link_to_results("scripts/08-summary/overview.pdf")`) and the [dynguidelines](https://www.github.com/dynverse/dynguidelines) app. _Not yet available_, but can be accessed in the results folder.
